### 2017-11-07 submission/manuscript.Rmd
update supplemental refs in text

***Using the Whole Community Increases Model AUC over CRC Associated Genera:***
For both fecal and tissue samples (matched and unmatched) there was a decrease in AUC when only OTUs from the CRC associated genera are used [Figure 4 & 5]. This decrease is observed in both adenoma and carcinoma groups [Figure 4 & 5]. The genus models generally had similar trends as observed for the OTU based models with the full genera models performing better then the CRC associated genera models [Figure S4-S5]. Both genus models perform similarily in their ability to be able to predict lesion (adenoma or carcinoma) with carcinoma having a higher AUC then adenoma [Figure S6-S8]. Matched tissue samples for those with carcinoma had an AUC that was more similar to the adenoma models [Figure S6A, S7B, & S8] then carcinoma models [Figure S6B & S7A].

>>>>

***Using the Whole Community Increases Model AUC over CRC Associated Genera:***
For both fecal and tissue samples (matched and unmatched) there was a decrease in AUC when only OTUs from the CRC associated genera are used [Figure 4 & 5]. This decrease is observed in both adenoma and carcinoma groups [Figure 4 & 5]. The genus models generally had similar trends as observed for the OTU based models with the full genera models performing better then the CRC associated genera models [Figure S2-S3]. Both genus models perform similarily in their ability to be able to predict lesion (adenoma or carcinoma) with carcinoma having a higher AUC then adenoma [Figure S4-S5]. Matched tissue samples for those with carcinoma had an AUC that was more similar to the adenoma models [Figure S4A, S5B, & S6] then carcinoma models [Figure S4B & S5A].

### 2017-11-07 submission/manuscript.tex
update supplemental refs in text

\textbf{\emph{Using the Whole Community Increases Model AUC over CRC
Associated Genera:}} For both fecal and tissue samples (matched and
unmatched) there was a decrease in AUC when only OTUs from the CRC
associated genera are used {[}Figure 4 \& 5{]}. This decrease is
observed in both adenoma and carcinoma groups {[}Figure 4 \& 5{]}. The
genus models generally had similar trends as observed for the OTU based
models with the full genera models performing better then the CRC
associated genera models {[}Figure S4-S5{]}. Both genus models perform
similarily in their ability to be able to predict lesion (adenoma or
carcinoma) with carcinoma having a higher AUC then adenoma {[}Figure
S6-S8{]}. Matched tissue samples for those with carcinoma had an AUC
that was more similar to the adenoma models {[}Figure S6A, S7B, \& S8{]}
then carcinoma models {[}Figure S6B \& S7A{]}.

>>>>

\textbf{\emph{Using the Whole Community Increases Model AUC over CRC
Associated Genera:}} For both fecal and tissue samples (matched and
unmatched) there was a decrease in AUC when only OTUs from the CRC
associated genera are used {[}Figure 4 \& 5{]}. This decrease is
observed in both adenoma and carcinoma groups {[}Figure 4 \& 5{]}. The
genus models generally had similar trends as observed for the OTU based
models with the full genera models performing better then the CRC
associated genera models {[}Figure S2-S3{]}. Both genus models perform
similarily in their ability to be able to predict lesion (adenoma or
carcinoma) with carcinoma having a higher AUC then adenoma {[}Figure
S4-S5{]}. Matched tissue samples for those with carcinoma had an AUC
that was more similar to the adenoma models {[}Figure S4A, S5B, \& S6{]}
then carcinoma models {[}Figure S4B \& S5A{]}.
